### 2023-01-03 cv/cv-body.tex
Add preprint
Add CCE paper
Add paper
Update CV

\begin{description}
\tightlist
\item[2021--22]
Research Scientist, Stock Assessment and Research Division, Pacific
Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, Canada
\item[2019--22]
Associate Editor, the Canadian Journal of Fisheries and Aquatic Sciences
\item[2020--22]
Adjunct Professor, Department of Mathematics, Simon Fraser University
\item[2017--20]
Program Head in Analytical Approaches and Spatial Stock Assessment,
Groundfish Section, Stock Assessment and Research Division, Pacific
Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, Canada
\item[2015--17]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, WA
\item[2015]
Postdoctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie University
\end{description}

@@

\begin{description}
\tightlist
\item[2022]
\textbf{Anderson, S.C.}, E.J. Ward, P.A. English, L.A.K. Barnett.
sdmTMB: an R package for fast, flexible, and user-friendly generalized
linear mixed effects models with spatial and spatiotemporal random
fields. bioRxiv 2022.03.24.485545.
\url{https://doi.org/10.1101/2022.03.24.485545}.
\item[2021]
\textbf{Anderson, S.C}, B.M. Connors, P.A. English, R.E. Forrest, R.
Haigh, K.R. Holt. Trends in Pacific Canadian groundfish stock status.
bioRxiv 2021.12.13.472502.
\url{https://doi.org/10.1101/2021.12.13.472502}.
\end{description}

@@

Essington, T. E. \textbf{S.C. Anderson}, L.A.K. Barnett, H.M. Berger,

@@

using thresholds and a physiologically based index. In press at
Ecography. \url{https://doi.org/10.1111/ecog.06249}.

@@

explicit species distribution models affect predictions. PeerJ 10:

@@

Science 9(1): 211710. \url{https://doi.org/10.1098/rsos.211710}.

@@

time series. Methods in Ecology and Evolution. In press.

@@

Fisheries. 23(1) 239--255. \url{https://doi.org/10.1111/faf.12613}. Open
access preprint: \url{https://doi.org/10.32942/osf.io/b87ng}.

@@

control measures? In press at Epidemics.

@@

frequency. In press at Fish and Fisheries.

@@

package}, \href{https://github.com/ss3sim/ss3sim}{code}.

@@

\begin{description}
\tightlist
\item[2021]
DFO. Status Update of Pacifc Cod (\emph{Gadus macrocephalus}) for West
Coast Vancouver Island (Area 3CD), and Hecate Strait and Queen Charlotte
Sound (Area 5ABCD) in 2020. DFO Can. Sci. Advis. Sec. Sci. Resp.
2021/002.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-fra.html}{French
version}).
\item[2021]
\textbf{Anderson, S.C.}, R.E. Forrest, Q.C. Huynh, E.A. Keppel. A
management procedure framework for groundﬁsh in British Columbia. DFO
Can. Sci. Advis. Sec. Res. Doc. 2021/007.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-eng.html}{Research
Document}).
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/SAR-AS/2021/2021_002-eng.html}{Associated
Science Advisory Report}.
\item[2020]
Haggarty D.R., Q.C. Huynh, R.E. Forrest, \textbf{S.C. Anderson}, M.J.
Bresch, E.A. Keppel. Evaluation of potential rebuilding strategies for
Inside Yelloweye Rockfish (\emph{Sebastes ruberrimus}) in British
Columbia. In Press. Accepected as a DFO Can. Sci. Advis. Sec. Res. Doc.
on June 11 2020.
\item[2020]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. DFO Can. Sci. Advis. Sec. Res. Doc. 2020/070 iv +
204 p.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-fra.html}{French
version}).
\item[2019]
\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards, 2019. A reproducible
data synopsis for over 100 species of British Columbia groundfish. DFO
Can. Sci. Advis. Sec. Res. Doc. 2019/041. vii + 321 p.
(\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-eng.html}{English
version},
\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-fra.html}{French
version}).
\end{description}

@@

\begin{description}
\tightlist
\item[2020--21]
Co-principal Investigator on NOAA Office of Science and Technology
NMFS-DFO grant ``Characterizing range shifts in groundfish species in
response to local climate velocities''. An extension to apply methods
from a similarly titled ACCASP grant below to NOAA waters. (\$30K USD)
\item[2020--21]
Collaborator on NOAA Office of Science and Technology NMFS-DFO grant
``Groundfish distribution shifts between British Columbia, Canada, and
Southeast Alaska, USA: climate drivers, ecosystem impacts and management
implications''. (\$30K USD)
\item[2019]
Canadian Journal of Fisheries and Aquatic Sciences Stevenson
Lectureship. \url{http://www.nrcresearchpress.com/page/cjfas/award} A
``lectureship conferred upon a young, energetic and creative researcher
at the cutting edge of an aquatic discipline''.
\item[2018--20]
Principal Investigator of a two-year grant from Fisheries and Oceans
Canada's Aquatic Climate Change Adaptation Services Program (ACCASP).
Project title: Characterizing range shifts in British Columbia
groundfish species in response to local climate velocities.
\item[2017]
Canadian Society for Ecology and Evolution (CSEE) Early Career Award.\\
\url{http://csee-scee.ca/2017-early-career-awards/}
\item[2015]
David H. Smith Conservation Postdoctoral Research Fellowship\\
\url{http://conbio.org/mini-sites/smith-fellows/meet-the-fellows/2015-fellows/sean-anderson}
\item[2015]
Simon Fraser University Dean of Graduate Studies Convocation Medal\\
\url{https://www.sfu.ca/dean-gradstudies/blog/year/2015/06/SeanAnderson.html}
\item[2014]
Garfield Weston Foundation / BC Packers Ltd.\ Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}

>>>>

\begin{description}
\tightlist
\item[2021--23]
Research Scientist, Stock Assessment and Research Division, Pacific
Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, Canada
\item[2019--23]
Associate Editor, the Canadian Journal of Fisheries and Aquatic Sciences
\item[2020--23]
Adjunct Professor, Department of Mathematics, Simon Fraser University
\item[2017--20]
Program Head in Analytical Approaches and Spatial Stock Assessment,
Groundfish Section, Stock Assessment and Research Division, Pacific
Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, Canada
\item[2015--17]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, WA
\item[2015]
Postdoctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie University
\end{description}

@@

\begin{description}
\tightlist
\item[2022]
Lindmark, M., \textbf{S.C. Anderson}, M. Gogina, M. Casini. Evaluating
drivers of spatiotemporal individual condition of a bottom-associated
marine fish. bioRxiv 2022.04.19.488709.
\url{https://doi.org/10.1101/2022.04.19.488709}.
\item[2022]
\textbf{Anderson, S.C.}, E.J. Ward, P.A. English, L.A.K. Barnett.
sdmTMB: an R package for fast, flexible, and user-friendly generalized
linear mixed effects models with spatial and spatiotemporal random
fields. bioRxiv 2022.03.24.485545.
\url{https://doi.org/10.1101/2022.03.24.485545}.
\item[2021]
\textbf{Anderson, S.C}, B.M. Connors, P.A. English, R.E. Forrest, R.
Haigh, K.R. Holt. Trends in Pacific Canadian groundfish stock status.
bioRxiv 2021.12.13.472502.
\url{https://doi.org/10.1101/2021.12.13.472502}.
\end{description}

@@

Ward, E.J., L.A.K. Barnett, \textbf{S.C. Anderson}, C.J.C. Commander,
T.E. Essington. Incorporating non-stationary spatial variability into
dynamic species distribution models. ICES Journal of Marine Science.
79(9): 2422-2429. \url{https://doi.org/10.1093/icesjms/fsac179}.
Essington, T.E. \textbf{S.C. Anderson}, L.A.K. Barnett, H.M. Berger,

@@

using thresholds and a physiologically based index. Ecography 2022(8):
e06249. \url{https://doi.org/10.1111/ecog.06249}.
Thompson, P.L., \textbf{S.C. Anderson}, J. Nephin, D.R. Haggarty, M.
Angelica Peña, P.A. English, K.S.P. Gale, E. Rubidge. Disentangling the
impacts of environmental change and commercial fishing on demersal fish
biodiversity in a northeast Pacific ecosystem. Marine Ecology Progress
Series. 689:137-154. \url{https://doi.org/10.3354/meps14034}.
Hunsicker, M.E., E.J. Ward, M.A.\ Litzow, \textbf{S.C. Anderson}, C.J.
Harvey, J.C. Field, J. Gao, M.G. Jacox, S. Melin, A.R. Thompson, P.
Warzybok. Tracking and forecasting community responses to climate
perturbations in the California Current Ecosystem. PLOS Climate. 1(3):
e0000014. \url{https://doi.org/10.1371/journal.pclm.0000014}.

@@

explicit species distribution models affect predictions. PeerJ. 10:

@@

Science. 9(1): 211710. \url{https://doi.org/10.1098/rsos.211710}.

@@

time series. Methods in Ecology and Evolution. 13(4):908-918.

@@

Fisheries. 23(1) 239--255. \url{https://doi.org/10.1111/faf.12613}.
{[}\href{https://www.dropbox.com/s/cmkzlxgiez6rzc0/English_etal_2022_contrasting_climate_velocity.pdf?dl=1}{PDF}{]}

@@

control measures? Epidemics. 35: 100453.

@@

frequency. Fish and Fisheries. 21(3):663-679.

@@

package}, \href{https://github.com/ss3sim/ss3sim}{code}).

@@

2022 Grandin, C.J., \textbf{S.C. Anderson}, P.A. English. Arrowtooth
Flounder (\emph{Atheresthes stomias}) Stock Assessment for the West
Coast of British Columbia in 2021. Accepted DFO Can. Sci. Advis. Sec.
Res. Doc.

2022 DFO. A data synopsis for British Columbia groundfish: 2021 data
update. DFO Can. Sci. Advis. Sec. Sci. Resp. 2022/020.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2022/2022_020-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2022/2022_020-fra.html}{French
version}).

\begin{description}
\tightlist
\item[2021]
DFO. Status Update of Pacifc Cod (\emph{Gadus macrocephalus}) for West
Coast Vancouver Island (Area 3CD), and Hecate Strait and Queen Charlotte
Sound (Area 5ABCD) in 2020. DFO Can. Sci. Advis. Sec. Sci. Resp.
2021/002.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-fra.html}{French
version}).
\item[2021]
\textbf{Anderson, S.C.}, R.E. Forrest, Q.C. Huynh, E.A. Keppel. A
management procedure framework for groundﬁsh in British Columbia. DFO
Can. Sci. Advis. Sec. Res. Doc. 2021/007.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-eng.html}{Research
Document}).
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/SAR-AS/2021/2021_002-eng.html}{Associated
Science Advisory Report}.
\item[2021]
Haggarty D.R., Q.C. Huynh, R.E. Forrest, \textbf{S.C. Anderson}, M.J.
Bresch, E.A. Keppel. Evaluation of potential rebuilding strategies for
Inside Yelloweye Rockfish (\emph{Sebastes ruberrimus}) in British
Columbia. DFO Can. Sci. Advis. Sec. Res. Doc. 2021/008.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_008-eng.html}{Research
Document}).
\item[2020]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. DFO Can. Sci. Advis. Sec. Res. Doc. 2020/070 iv +
204 p.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-fra.html}{French
version}).
\item[2019]
\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards, 2019. A reproducible
data synopsis for over 100 species of British Columbia groundfish. DFO
Can. Sci. Advis. Sec. Res. Doc. 2019/041. vii + 321 p.
(\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-eng.html}{English
version},
\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-fra.html}{French
version}).
\end{description}

@@

\begin{description}
\tightlist
\item[2020--21]
Co-principal Investigator on NOAA Office of Science and Technology
NMFS-DFO grant ``Characterizing range shifts in groundfish species in
response to local climate velocities''. An extension to apply methods
from a similarly titled ACCASP grant below to NOAA waters.
\item[2020--21]
Collaborator on NOAA Office of Science and Technology NMFS-DFO grant
``Groundfish distribution shifts between British Columbia, Canada, and
Southeast Alaska, USA: climate drivers, ecosystem impacts and management
implications''.
\item[2019]
Canadian Journal of Fisheries and Aquatic Sciences Stevenson
Lectureship. \url{http://www.nrcresearchpress.com/page/cjfas/award} A
``lectureship conferred upon a young, energetic and creative researcher
at the cutting edge of an aquatic discipline''.
\item[2018--20]
Principal Investigator of a two-year grant from Fisheries and Oceans
Canada's Aquatic Climate Change Adaptation Services Program (ACCASP).
Project title: Characterizing range shifts in British Columbia
groundfish species in response to local climate velocities.
\item[2017]
Canadian Society for Ecology and Evolution (CSEE) Early Career Award.\\
\url{http://csee-scee.ca/2017-early-career-awards/}
\item[2015]
David H. Smith Conservation Postdoctoral Research Fellowship\\
\url{http://conbio.org/mini-sites/smith-fellows/meet-the-fellows/2015-fellows/sean-anderson}
\item[2015]
Simon Fraser University Dean of Graduate Studies Convocation Medal\\
\url{https://www.sfu.ca/dean-gradstudies/blog/year/2015/06/SeanAnderson.html}
\item[2014]
Garfield Weston Foundation / BC Packers Ltd.\ Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}
